\newpage

# (PART) Méthodes {-}

# Méthodes

We describe our methods in this chapter.

When you subset a data frame, it does not necessarily return
a data frame. For example, if you subset two columns, you get
a data frame, but when you try to subset one column, you get
a vector:

```{r class.source="bg-danger", class.output="bg-warning"}
mtcars[1:5, "mpg"]
```

To make sure that we always get a data frame, we have to use
the argument `drop = FALSE`. Now we use the chunk option
`class.source = "bg-success"`.

```{r df-drop-ok, class.source="bg-success"}
mtcars[1:5, "mpg", drop = FALSE]
```

Then we assign a class `watch-out` to the code chunk via the
chunk option `class.source`.

```{r class.source="watch-out"}
mtcars[1:5, "mpg"]
```

```{css, echo=FALSE}
pre {
  max-height: 300px;
  overflow-y: auto;
}

pre[class] {
  max-height: 100px;
}
```

We have defined some CSS rules to limit the height of
code blocks. Now we can test if these rules work on code
blocks and text output:

```{r}
# pretend that we have a lot of code in this chunk
if (1 + 1 == 2) {
  # of course that is true
  print(mtcars)
  # we just printed a lengthy data set
}
```

Next we add rules for a new class `scroll-100` to limit
the height to 100px, and add the class to the output of
a code chunk via the chunk option `class.output`:

```{css, echo=FALSE}
.scroll-100 {
  max-height: 100px;
  overflow-y: auto;
  background-color: inherit;
}
```

```{r, class.output="scroll-100"}
print(mtcars)
```

