\newpage

# (PART) Résultats {-}

# Résultats

Some _significant_ applications are demonstrated in this chapter.

L’article 55 de la loi SRU de 2002 vise à promouvoir la mixité sociale en imposant un seuil de logements sociaux (20 %, passé en 2013 à 25 %) aux communes des grandes agglomérations. Une étude dans le département des Yvelines montre que les villes déficitaires en logement social s’accommodent finalement bien de ces objectifs mais que la mixité sociale n’est toujours pas au rendez-vous.




```{r}

library(data.table) 
library(dplyr)
library(sf)
library(stringr)
library(ggmap)
library(leaflet)

# Fonctions Utils
source('R/fonctionS_utils.R')

df <- FiltrerZone(cheminFichierCSV = Filosofi2015_carreaux_200m_metropole, depcom = '44109')
save(df,file = 'data/carreaux_insee_nantes.RData')

rpls_2019_nantes <- fread('extdata/rpls_geoloc_2019/RPLS2019_detail_reg52.csv') %>% 
  filter(DEPCOM == '44109')
save(rpls_2019_nantes,file = 'data/rpls_2019_nantes.RData')

# Saint herblaiN codeDep = 44162
#locs <- c('6 Chemin de la chatterie, 44800 Saint-Herblain, FRANCE')

locs <- c('22 place viarme , 44000 Nantes, FRANCE')
register_google(key = "")
geo = geocode(locs)

m <- leaflet() %>%
  setView(geo$lon, geo$lat, zoom = 18) %>% 
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lng=geo$lon, lat=geo$lat, popup="6 Chemin de la chatterie, 44800 Saint-Herblain")
m  # Print the map

#zones <- FiltrerZones(Filosofi2015_carreaux_200m_metropole_shp, '44109')

calcuTotal <- df %>%
  dplyr::summarise(sum)

mapview::mapview(df, zcol = "Depcom", legende = F)

#test <- FiltrerZones(Filosofi2015_carreaux_200m_metropole, Filosofi2015_carreaux_200m_metropole_shp, '44109')
#test <- calculAgregatsZones(Filosofi2015_carreaux_200m_metropole_shp,Filosofi2015_carreaux_200m_metropole,  c("44109"), c("Ind_40_54","Ind_55_64"))

```


This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).


```{r}
library(dygraphs)
lungDeaths <- cbind(mdeaths, fdeaths)
dygraph(lungDeaths)

dygraph(lungDeaths) %>% dyRangeSelector()

dygraph(lungDeaths) %>%
  dySeries("mdeaths", label = "Male") %>%
  dySeries("fdeaths", label = "Female") %>%
  dyOptions(stackedGraph = TRUE) %>%
  dyRangeSelector(height = 20)

hw <- HoltWinters(ldeaths)
predicted <- predict(hw, n.ahead = 72, prediction.interval = TRUE)

dygraph(predicted, main = "Predicted Lung Deaths (UK)") %>%
  dyAxis("x", drawGrid = FALSE) %>%
  dySeries(c("lwr", "fit", "upr"), label = "Deaths") %>%
  dyOptions(colors = RColorBrewer::brewer.pal(3, "Set1"))

#knitr::included_url('miniUI')
#knitr::include_app('miniUI/app.R', height = '600px')

```


## Inputs and Outputs 

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.
